---
title: "EDA of Titanic Passenger List"
author: "Derick Carlson"
date: "2023-05-11"
---

# Assignment Part I: Examples of adding styles

#### Links

**The original original source of data can downloaded using this link**  
https://public.tableau.com/app/sample-data/titanic%20passenger%20list.csv

#### Unordered Lists

*The most common plotting packages in R are:*

* base
* lattice
* ggplot2

*but not *~~Excel~~

# Assignment Part II: Titanic EDA using RMD
**The original original source of data can downloaded using this link**  
https://public.tableau.com/app/sample-data/titanic%20passenger%20list.csv

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) 
titanic <- read.csv("TitanicPassengerList.csv", stringsAsFactors = FALSE)
```
## Part I: Handling Missing Values

```{r include=FALSE}
naage <- sum(is.na(titanic$age))

titanic <- titanic %>%
  filter(!is.na(age))
```

```{r include=FALSE}
rowct <- nrow(titanic)
```

There are `r rowct` observations left after omitting `r naage` blank ages.

## Part III: Summary Statistics

The mean age of the Titanic passengers is `r mean(titanic$age)`.

```{r include=FALSE}
female_df <- titanic %>%
  filter(sex == "female") 

female_count <- nrow(female_df)
f_mean_age <- mean(female_df$age)

male_df <- titanic %>%
  filter(sex == "male") 

male_count <- nrow(male_df)
m_mean_age <- mean(male_df$age) 
```
`r female_count` females survived, averaging age `r f_mean_age`.

`r male_count` males survived, averaging age `r m_mean_age`.

## Part IV: Age Distribution

```{r}
ggplot(titanic, aes(x = age)) +
  geom_histogram(binwidth = 5, fill = "steelblue", color = "white") +
  labs(title = "Age Distribution of Titanic Passengers",
       subtitle = "Histogram of Ages",
       x = "Age",
       y = "Count")
```


